---
title: "RWorksheet_Vicinte#2"
author: "Anthony Dave S. Vicinte"
date: "2024-09-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Create a vector using : operator
# a. Sequence from -5 to 5
```{r}
vector_a <- -5:5
print(vector_a)

```

# Describe its output: This will create a vector containing integers from -5 to 5.
# b. x <- 1:7
```{r}
x <- 1:7
print(x)
```
# The value of x are: 1 2 3 4 5 6 7
# 2. Create a vector using seq() function
# a. seq(1, 3, by=0.2)
```{r}
vector_b <- seq(1, 3, by=0.2)
print(vector_b)
```
# Write the R script and its output: This creates a sequence from 1 to 3 with a step size of 0.2.
# 3. A factory has a census of its workers. There are 50 workers in total. The following list shows their ages: 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18.
```{r}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
          22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37,
          43, 53, 41, 51, 35, 24, 33, 41, 53, 40, 18, 44, 38,
          41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)
```
#a. Access 3rd element, what is the value? 
```{r}
third_element <- ages[3]
print(third_element)
```
#b. Access 2nd and 4th element, what are the values?
```{r}
second_fourth_elements <- ages[c(2, 4)]
print(second_fourth_elements)
```
#c. Access all but the 4th and 12th element is not included.
```{r}
not4th2th <- ages[-c(4, 12)]
print(not4th2th)
```
#4. *Create a vector x <- c("first"=3, "second"=0, "third"=9). Then named the vector, names(x).
```{r}
x <- c("first" = 3, "second" = 0, "third" = 9)
print(x)
```
#a. Print the results. Then access x[c("first", "third")].
```{r}
first_third <- x[c("first", "third")]
print(first_third)
```
#Describe the output: This outputs the values along with the names "first" and "third".
#5. Create a sequence x from -3:2.
```{r}
x <- -3:2
```
#a. Modify 2nd element and change it to 0;
```{r}
x[2] <- 0
print(x)
```
#Describe the output:his will show the modified vector with the second element set to 0.
#6. *The following data shows the diesel fuel purchased by Mr. Cruz. 
#Month Jan Feb March Apr May June
#Price per liter (PhP) 52.50 57.25 60.00 65.00 74.25 54.00
#Purchase–quantity(Liters) 25 30 40 50 10 45
```{r}
months <- c("Jan", "Feb", "Mar", "Apr", "May", "Jun")
Theprices <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00)
quantities <- c(25, 30, 40, 50, 10, 45)
```
#a. Create a data frame for month, price per liter (php) and purchase-quantity (liter). Write the R scripts and its output.
```{r}
fuel_data <- data.frame(Month = months, Price_per_Liter = Theprices, Purchase_Quantity = quantities)
print(fuel_data)
```
#b. What is the average fuel expenditure of Mr. Cruz from Jan to June? Note: Use ‘weighted.mean(liter, purchase)‘. Write the R scripts and its output.
```{r}
average_expenditure <- weighted.mean(Theprices, quantities)
print(average_expenditure)
```
#7. R has actually lots of built-in datasets. For example, the rivers data “gives the lengths (in miles) of 141 “major” rivers in North America, as compiled by the US Geological Survey”. 
#a. Type “rivers” in your R console.
#Create a vector data with 7 elements, containing the number of elements (length) in rivers, their sum (sum), mean (mean), median(median), variance(var), standard deviation(sd), minimum (min) and maximum (max).
#data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers), sd(rivers), min(rivers), max(rivers))
```{r}
data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers),
          sd(rivers), min(rivers), max(rivers))
print(data)
```
#b. What are the results?
# The results will show various statistics about the rivers data.
#8. The table below gives the 25 most powerful celebrities and their annual pay as ranked by the editions of Forbes magazine and as listed on the Forbes.com website.
#a. Create vectors according to the above table. Write the R scripts and its output.
```{r}
celebrity_names <- c("Kylie Jenner", "Kanye West", "Taylor Swift", "Dwayne Johnson",
                     "J.K. Rowling", "Rihanna", "Dr. Phil", "Ellen DeGeneres", 
                     "James Patterson", "LeBron James", "Billie Eilish", "Cristiano Ronaldo", 
                     "Lionel Messi", "Kevin Durant", "Tiger Woods", "Judd Apatow", 
                     "Howard Stern", "Sofia Vergara", "Mark Wahlberg", "Beyoncé", 
                     "Oprah Winfrey", "Rafael Nadal", "Shakira", "Kim Kardashian", 
                     "Jeffree Star")
power_ranking <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25)
annual_pay <- c(590, 170, 150, 87.5, 60, 45, 95, 84, 80, 87, 50, 105, 130, 50, 35, 20, 15, 80, 50, 60, 45, 25, 40, 30, 25)
celebrity_names
power_ranking
annual_pay
CombineThe3 <- c(celebrity_names, power_ranking,annual_pay)
```
#b. Modify the power ranking and pay of J.K. Rowling. Change power ranking to 15 and pay to 90. Write the R scripts and its output. 
```{r}
Rowling <- which(celebrity_names == "J.K. Rowling")
power_ranking[Rowling] <- 15
annual_pay[Rowling] <- 90
power_ranking
annual_pay
```
#c. Create an excel file from the table above and save it as csv file(PowerRanking). Import the csv file into  the RStudio. What is the R script?
```{r}
Celeb <- write.csv("CombineThe3", "combinethe3.csv", row.names=FALSE)
Celeb
```
#d. Access the rows 10 to 20 and save it as Ranks.RData. Write the R script and its output.
```{r}
Ranks <- Celeb[10:20,]
save(Ranks, file = "Ranks.RData")
Ranks
```
#e. Describe its output: The output is Celeb starting from rows 10 to 20
#9. Download the Hotels-Vienna https://tinyurl.com/Hotels-Vienna
#a. Import the excel file into your RStudio. What is the R script?
```{r}
library("openxlsx")
library("readxl")
data_set <- read_xlsx("hotels-vienna.xlsx")
data_set
```
#b. How many dimensions does the dataset have? What is the R script? WHat is its output?
```{r}
dimensions <- dim(data_set)
dimensions
```
#c. Select columns country, neighbourhood, price, stars, accomodation_type, and ratings. Write the R script.
```{r}
selected_data <- data_set[, c("country", "neighbourhood", "price","stars", "accommodation_type", "rating")]
selected_data
```
#d. Save the data as **new.RData to your RStudio. Write the R script.
```{r}
save(selected_data, file = "new.RData")
```
#e. Display the first six rows and last six rows of the new.RData. What is the R script?
```{r}
head(selected_data)
tail(selected_data)
```
#10. Create a list of ten (10) vegetables you ate during your lifetime. If none, just list down.
#a. Write the R scripts and its output.
```{r}
vegetables <- list("Eggplant", "Carrots", "Potato", "Lettuce", "Cabbage", "Garlic", "Onion", "Mushroom", "Pumpkin", "Ginger")
vegetables
```
#b. Add 2 additional vegetables after the last vegetables in the list. What is the R script and its output?
```{r}
vegetables <- append(vegetables, list("Mung Beans", "Drumstick Tree"))
vegetables
```
#c. Add 4 additional vegetables after index 5. How many datapoints does your vegetable list have? What is the R script and its output?
```{r}
vegetables <- append(vegetables, list("Chayote", "Snow Cabbage", "Bitter Gourd", "Broccoli"))
vegetables
length(vegetables)
```
#d. Remove the vegetables in index 5, 10, and 15. How many vegetables were left? Write the codes and its output.
```{r}
vegetables <- vegetables[-c(5, 10, 15)]
vegetables
length(vegetables)
```

