---
title: "RWorksheet_VIcinte#4a"
author: "Anthony Dave Vicinte"
date: "2024-10-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1. The table below shows the data about shoe size and height. Create a data frame.
```{r}
Hhdata <- read.csv("/cloud/project/RWorksheet4a/Household Data.csv")
Hhdata
```
#a. Describe the data.
#The data consist of Shoe size, Height and Gender.

#b. Create a subset by males and females with their corresponding shoe size and height. What its result? Show the R scripts.
```{r}
MF <- subset(Hhdata, Gender == "M" & Shoe.size & Height)
MF
```
```{r}
FM <- subset(Hhdata, Gender == "F" & Shoe.size & Height)
FM
```
#c. Find the mean of shoe size and height of the respondents. Write the R scripts and its result.
```{r}
meanSs <- mean(Hhdata$Shoe.size)
meanH <- mean(Hhdata$Height)
meanSs
meanH
```
#d. Is there a relationship between shoe size and height? Why?

# yes they have relationship. If the male have the same height there are times that they are not equal in shoe size same with female but when it comes to both gender have the same height it's noticable that male always have a larger shoe size than female.

#2.
```{r}
months <- c("March","April","January","November","January",
"September","October","September","November","August",
"January","November","November","February","May","August","July","December","August","August","September","November","February","April")
months
```
```{r}
factor_months_vector <- factor(months)
factor_months_vector
```
#3.
```{r}
SummaryM <- summary(months)
SummaryM
```

```{r}
SummaryF <- summary(factor_months_vector)
SummaryF
```
#4.
```{r}
direction <- c("East", "West", "North")
Frequency <- c(1,4,3)
factor_data <- data.frame(direction,Frequency)
factor_data
```
```{r}
new_order_data <- factor(factor_data,levels = c("East","West","North"))
new_order_data
```
#5.
#a. Import the excel file into the Environment Pane using read.table() function. Write the code.
```{r}
readTable <- read.table("import_march.csv", header=TRUE, sep=",")
readTable
```
#b. View the dataset. Write the R scripts and its result.
```{r}
print(readTable)
```
```{r}
#6.
#a.
num <- as.numeric(readline(prompt="Select a number between 1 to 50:"))
if (!is.na(num)>=1 && num<=50){
  cat(num)
  }else {
  print("The number selected is beyond the range of 1 to 50.")
}
if(!is.na(num)==20){
  print("TRUE")
}else {
  cat(num)
}
```
#7.
```{r}
Theprice <- as.numeric(readline(prompt="Enter Price: "))
minimum <- function(Theprice) {
  bills <- 0
  
  if (!is.na(Theprice) >= 1000) {
    bills <- bills + Theprice %/% 1000
    Theprice <- Theprice %% 1000
  }
  if (!is.na(Theprice) >= 500) {
    bills <- bills + Theprice %/% 500
    Theprice <- Theprice %% 500
  }
  if (!is.na(Theprice) >= 200) {
    bills <- bills + Theprice %/% 200
    Theprice <- Theprice %% 200
  }
  if (!is.na(Theprice) >= 100) {
    bills <- bills + Theprice %/% 100
    Theprice <- Theprice %% 100
  }
  if (!is.na(Theprice) >= 50) {
    bills <- bills + Theprice %/% 50
    Theprice <- Theprice %% 50
  }
  return(bills)
}
minimum(Theprice)
```
#8.
```{r}
#a.
Grades <- data.frame(
Name=c("Annie","Thea","Steve","Hanna"),
Grade1=c(85,65,75,95),
Grade2=c(65,75,55,75),
Grade3=c(85,90,80,100),
Grade4=c(100,90,85,90)
)
Grades
```
```{r}
#b.
Annie <- (Grades$Grade1[1] + Grades$Grade2[1] + Grades$Grade3[1] + Grades$Grade4[1]) / 4
if (Annie > 90) {
  cat("Annie's average grade this semester is", Annie)
}
  Thea <- (Grades$Grade1[2] + Grades$Grade2[2] + Grades$Grade3[2] + Grades$Grade4[2]) / 4
if (Thea > 90) {
  cat("Annie's average grade this semester is", Thea)
}
  Steven <- (Grades$Grade1[3] + Grades$Grade2[3] + Grades$Grade3[3] + Grades$Grade4[3]) / 4
if (Steven > 90) {
  cat("Annie's average grade this semester is", Steven)
}
  Hanna <- (Grades$Grade1[3] + Grades$Grade2[3] + Grades$Grade3[3] + Grades$Grade4[3]) / 4
if (Hanna > 90) {
  cat("Annie's average grade this semester is", Hanna)
}else{
  print("No students exceeds 90")
}
```
```{r}
#c.
Grade1ave <- sum(Grades$Grade1) / 4
if (Grade1ave < 80) {
  cat("The Grade1 test was difficult with an average score of", Grade1ave)
}
Grade2ave <- sum(Grades$Grade2) / 4
if (Grade2ave < 80) {
  cat("The Grade1 test was difficult with an average score of", Grade2ave)
}
Grade3ave <- sum(Grades$Grade3) / 4
if (Grade3ave < 80) {
  cat("The Grade1 test was difficult with an average score of", Grade3ave)
}
Grade4ave <- sum(Grades$Grade4) / 4
if (Grade4ave < 80) {
  cat("The Grade1 test was difficult with an average score of", Grade4ave)
}
```
```{r}
#d.
Annie_highest <- Grades$Grade1[1]
if (Grades$Grade2[1] > Annie_highest) Annie_highest <- Grades$Grade2[1]
if (Grades$Grade3[1] > Annie_highest) Annie_highest <- Grades$Grade3[1]
if (Grades$Grade4[1] > Annie_highest) Annie_highest <- Grades$Grade4[1]
if (Annie_highest > 90) {
   cat("Annie's highest grade this semester is", Annie_highest,"\n")
}
Thea_highest <- Grades$Grade1[2]
if (Grades$Grade2[2] > Thea_highest) Thea_highest <- Grades$Grade2[2]
if (Grades$Grade3[2] > Thea_highest) Thea_highest <- Grades$Grade3[2]
if (Grades$Grade4[2] > Thea_highest) Thea_highest <- Grades$Grade4[2]
if (Thea_highest > 90) {
   cat("Thea's highest grade this semester is", Thea_highest)
}
Steve_highest <- Grades$Grade1[3]
if (Grades$Grade2[3] > Steve_highest) Steve_highest <- Grades$Grade2[3]
if (Grades$Grade3[3] > Steve_highest) Steve_highest <- Grades$Grade3[3]
if (Grades$Grade4[3] > Steve_highest) Steve_highest <- Grades$Grade4[3]
if (Steve_highest > 90) {
   cat("Steve's highest grade this semester is", Steve_highest)
}
Hanna_highest <- Grades$Grade1[4]
if (Grades$Grade2[4] > Hanna_highest) Hanna_highest <- Grades$Grade2[4]
if (Grades$Grade3[4] > Hanna_highest) Hanna_highest <- Grades$Grade3[4]
if (Grades$Grade4[4] > Hanna_highest) Hanna_highest <- Grades$Grade4[4]
if (Hanna_highest > 90) {
   cat("Hanna's highest grade this semester is", Hanna_highest)
}
```


