---
title: "RWorksheet_Vicinte#3a"
author: "Anthony Dave Vicinte"
date: "2024-09-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1. There is a built-in vector LETTERS contains the uppercase letters of the alphabet and letters which contains the lowercase letters of the alphabet.
#LETTERS
```{r}
LETTERS
```
```{r}
letters
```
#Based on the above vector LETTERS:
#a. You need to produce a vector that contains the first 11 letters
```{r}
First11 <- LETTERS[1:11]
First11
```
#b. Produce a vector that contains the odd numbered letters.
```{r}
OddNumbered <- LETTERS[seq(1,26,by=2)]
OddNumbered
```
#c. Produce a vector that contains the vowels.
```{r}
Vowels <- LETTERS[c(1,5,9,15,21)]
Vowels
```
#d. Produce a vector that contains the last 5 lowercase letters.
```{r}
Last5 <- tail(letters,5)
Last5
```
#e. Produce a vector that contains letters between 15 to 24 letters in lowercase.
```{r}
Between <- letters[15:24]
Between
```
#2. Create a vector(not a dataframe) with the average temperatures in April for Tugue- garao City, Manila, Iloilo City, Tacloban, Samal Island, and Davao City. The average temperatures in Celcius are 42, 39, 34, 34, 30, and 27 degrees.
#a
```{r}
city <- c("Tuguegarao City", "Manila", "Iloilo City", "Tacloban", "Samal Island", "Davao City")
```
#b
```{r}
temp <- c(42, 39, 34, 34, 30, 27)
```

#c. Create a dataframe to combine the city and the temp by using ‘data.frame(). What the R code and its result?
```{r}
CombCityTemp <- data.frame(city, temp)
CombCityTemp
```
#d
```{r}
names(CombCityTemp) <- c("City", "Temperature")
CombCityTemp
```
#e.
```{r}
str(CombCityTemp)
#Describe the output: It shows the structure of the data frame.
```
#f.
```{r}
CombCityTemp[3:4, ]
```
#g.
```{r}
CombCityTemp[1, ]
CombCityTemp[6, ]
```
#Using Matrices
```{r}
matrix(c(5,6,7,4,3,2,1,2,3,7,8,9),nrow = 2)
```
```{r}
matrix(data = c(3,4,5,6,7,8),3,2)
```
```{r}
diag(1,nrow = 6,ncol = 5)
```
```{r}
diag(6)
```
#2. Create a matrix of one to eight and eleven to fourteen with four columns and three rows.
#a.
```{r}
Thematrix <- matrix(data = c(1,2,3,4,5,6,7,8,11,12,13,14),3,4)
Thematrix
```
#b.
```{r}
multiply <- Thematrix * 2
multiply
```
#c.
```{r}
r2 <- Thematrix[2, ]
r2
```
#d.
```{r}
multiply[1:2, 3:4]
```
#e.
```{r}
multiply[3, 2:3]
```
#f
```{r}
multiply[, 4]
```
#g.
```{r}
rownames(multiply) <- c("isa","dalawa","tatlo")

colnames(multiply) <- c("uno", "dos", "tres", "quatro")
multiply
```
#h.




