---
title: "RWorksheet_Vicinte#3b"
author: "Anthony Dave Vicinte"
date: "2024-09-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#1. Create a data frame using the table below.
#a.
```{r}
data <- data.frame(
  Respondents = 1:20,
  Sex = c(2, 1, 2, 2, 1, 1, 2, 2, 2, 1, 1, 2, 2, 1, 2, 2, 1, 2, 1, 2),
  Fathers_Occupation = c(1, 2, 3, 1, 2, 1, 3, 2, 3, 3, 1, 3, 2, 1, 3, 1, 3, 3, 1, 1),
  Persons_at_Home = c(5, 7, 3, 5, 5, 3, 6, 6, 7, 7, 3, 7, 4, 7, 8, 8, 3, 11, 8, 6),
  Siblings_at_School = c(6, 4, 3, 2, 3, 3, 5, 5, 4, 5, 3, 7, 5, 2, 1, 3, 1, 5, 3, 2),
  Types_of_Houses = c(1, 2, 3, 1, 3, 1, 3, 3, 3, 1, 3, 3, 3, 1, 3, 3, 3, 3, 3, 2)
)
```
#b.
```{r}
str(data)
summary(data)
```
#c.
```{r}
mean(data$Siblings_at_School)
```
#d.
```{r}
data[1:2, ]
```
#e.
```{r}
data[c(3, 5), c(2, 4)]
```
#f.
```{r}
types_houses <- data$Types_of_Houses
types_houses
```
#g.
```{r}
male_farmers <- data[data$Sex == 1 & data$Fathers_Occupation == 1, ]
male_farmers
```
#g.
```{r}
female_siblings <- data[data$Sex == 2 & data$Siblings_at_School >= 5, ]
female_siblings
```
#2. Write a R program to create an empty data frame. Using the following codes:
```{r}
df = data.frame(Ints=integer(),

Doubles=double(), Characters=character(),
Logicals=logical(),
Factors=factor(),
stringsAsFactors=FALSE)

print("Structure of the empty dataframe:")
print(str(df))
```
#a. Describe the results: The empty data frame has 5 columns: integers, doubles, characters, logicals, and factors, but no data is stored yet.
#3. Create a .csv file of this. Save it as HouseholdData.csv
#a
```{r}
data_csv <- read.csv("HouseholdData.csv")
```
#b.
```{r}
data$Sex <- as.integer(factor(data$Sex, levels = c("Male", "Female")))
```
#c.
```{r}
data$Types_of_Houses <- as.integer(factor(data$Types_of_Houses, levels = c("Wood", "Concrete", "Semi-Concrete")))
```
#d.
```{r}
data$Fathers_Occupation <- as.integer(factor(data$Fathers_Occupation, levels = c("Farmer", "Driver", "Others")))
```
#e.
```{r}
female_drivers <- data[data$Sex == 2 & data$Fathers_Occupation == 2, ]
female_drivers
```
#f.
```{r}
siblings_5_plus <- data[data$Siblings_at_School >= 5, ]
siblings_5_plus
```
#4. Interpret the graph.
#The graph shows the number of tweets per day from July 14 to July 21, 2020, categorized by sentiment (negative, neutral, and positive). On most days, negative tweets are the highest, followed by neutral and positive tweets.
